---
title: "ER Choice v. Usage - Study 3 Dataframe Creation"
author: "William J. Mitchell"
date: "`r Sys.Date()`"
output: html_document
---

# ----- SCRIPT START -----

Specifying our package usage
```{r Packages I Use}
   pacman::p_load(tidyverse)
```

Indicating how I want numbers presented and formatted
``` {r Number Formatting}
  options(scipen=100)
  options(digits=3)
  options(tinytex.verbose = TRUE)
```
  
```{r Setting Working Directories}
  # Identifying our main directory
  WorkDir <- "C:/Users/tui81100/Documents/GitHub/fright_night_study/"

  # Identifying specific directories to read and write from
  Export <- paste0(WorkDir, "data/Study_03/Raw/")
  Import <- paste0(WorkDir, "data/Study_03/Source/")
```

#  DATAFRAME CREATION 
  
```{r Loading dataframe}
  setwd(Import)
  df.temp <- read.csv(file = "df.csv", 
                 header = T, sep=",", 
                 stringsAsFactors = F,
                 na.strings=c("","N/A"))
```

Removing participants who did not consent, who did not complete, and who failed the attention check.
``` {r Removing Non-Completers, Non-Consenters}
  df.temp <- subset(df.temp, df.temp$Finished == "True" &
                             df.temp$Progress == "100" &
                             df.temp$Consent == "I consent to participating in this study" &
                             df.temp$Attention.Check == "Distraction")
```

Removing people who finished too quickly or too slowly as determined by a time registered as three standard deviation units above or below the average.
```{r Removing Folks Based on Time}
  df.temp <- subset(df.temp, 
                    abs(as.numeric(scale(as.numeric(df.temp$Duration), 
                                         center = T, 
                                         scale = T))) <= 3)
```

Removing rows with data we don't really need for the analysis
```{r Removing Superfluous columns}
  df.temp <- df.temp[,c(27,29:173,13,14)]
```
  
The standard PID is too clunky to be useful, so I'm creating a much smoother PID for each participant.  
```{r Adding a Cleaning PID}  
  df.temp$PID.FU <- c(paste("P00", seq(1,9,1), 
                         sep = ""), 
                   paste("P0", seq(10,99,1), 
                         sep = ""), 
                   paste("P", seq(100,length(rownames(df.temp)),1), 
                         sep = ""))
```

# MEASURE SCORING

``` {r Scoring ERQ}
for (i in 1:length(rownames(df.temp))){
  for (s in 89:98){
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Strongly disagree")
      df.temp[i,s] <- 1
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Disagree")
      df.temp[i,s] <- 2
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Somewhat disagree")
      df.temp[i,s] <- 3
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Neither agree nor disagree")
      df.temp[i,s] <- 4
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Somewhat agree")
      df.temp[i,s] <- 5
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Agree")
      df.temp[i,s] <- 6
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Strongly agree")
      df.temp[i,s] <- 7
    }
}

for (i in 89:98){
  df.temp[,i] <- as.numeric(df.temp[,i])
}

for (i in 1:length(rownames(df.temp))){
  df.temp$ERQ_Reapp.FU[i] <- sum(df.temp$ERQ01[i] + 
                              df.temp$ERQ03[i] + 
                              df.temp$ERQ05[i] + 
                              df.temp$ERQ07[i] + 
                              df.temp$ERQ08[i] + 
                              df.temp$ERQ10[i])
  df.temp$ERQ_Supp.FU[i] <- sum(df.temp$ERQ02[i] + 
                             df.temp$ERQ04[i] + 
                             df.temp$ERQ06[i] + 
                             df.temp$ERQ09[i])
}
```

``` {r Scoring DERS}
for (i in 1:length(rownames(df.temp))){
  for (s in 99:134){
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Almost never\n\n(00 - 10 %)\n")
      df.temp[i,s] <- 1
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Sometimes\n(11 – 35%)\n")
      df.temp[i,s] <- 2
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "About half the time\n(36 – 65%)\n")
      df.temp[i,s] <- 3
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Most of the time\n(66 – 90%)\n")
      df.temp[i,s] <- 4
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Almost always\n(91 – 100%)\n")
      df.temp[i,s] <- 5
    }
}

for (i in 99:134){
  df.temp[,i] <- as.numeric(df.temp[,i])
}

DERS.Reverse <- c(1,2,6,7,8,10,17,20,22,24,34)
for (i in DERS.Reverse){
  for (s in 1:length(rownames(df.temp))){
  df.temp[s,(98 + i)] <- sum(6 - df.temp[s,(98 + i)])
  }  
}

for (i in 1:length(rownames(df.temp))){
  df.temp$DERS.FU[i] <- sum(df.temp$DERS01[i] + df.temp$DERS02[i] + df.temp$DERS03[i] + df.temp$DERS04[i] + df.temp$DERS05[i] + df.temp$DERS06[i] +
                         df.temp$DERS07[i] + df.temp$DERS08[i] + df.temp$DERS09[i] + df.temp$DERS10[i] + df.temp$DERS11[i] + df.temp$DERS12[i] +
                         df.temp$DERS13[i] + df.temp$DERS14[i] + df.temp$DERS15[i] + df.temp$DERS16[i] + df.temp$DERS17[i] + df.temp$DERS18[i] +
                         df.temp$DERS19[i] + df.temp$DERS20[i] + df.temp$DERS21[i] + df.temp$DERS22[i] + df.temp$DERS23[i] + df.temp$DERS24[i] +
                         df.temp$DERS25[i] + df.temp$DERS26[i] + df.temp$DERS27[i] + df.temp$DERS28[i] + df.temp$DERS29[i] + df.temp$DERS30[i] +
                         df.temp$DERS31[i] + df.temp$DERS32[i] + df.temp$DERS33[i] + df.temp$DERS34[i] + df.temp$DERS35[i] + df.temp$DERS36[i])
  df.temp$DERS.Nonaccept.FU[i] <- sum(df.temp$DERS11[i] + df.temp$DERS12[i] + df.temp$DERS21[i] + df.temp$DERS23[i] + df.temp$DERS25[i] + df.temp$DERS29[i])
  df.temp$DERS.DiffGoal.FU[i] <- sum(df.temp$DERS13[i] + df.temp$DERS18[i] + df.temp$DERS20[i] + df.temp$DERS26[i] + df.temp$DERS33[i])
  df.temp$DERS.Impulse.FU[i] <- sum(df.temp$DERS03[i] + df.temp$DERS14[i] + df.temp$DERS19[i] + df.temp$DERS24[i] + df.temp$DERS27[i] + df.temp$DERS32[i])
  df.temp$DERS.LackAware.FU[i] <- sum(df.temp$DERS02[i] + df.temp$DERS06[i] + df.temp$DERS08[i] + df.temp$DERS10[i] + df.temp$DERS17[i] + df.temp$DERS34[i])
  df.temp$DERS.LimitAccess.FU[i] <- sum(df.temp$DERS15[i] + df.temp$DERS16[i] + df.temp$DERS22[i] + df.temp$DERS28[i] + df.temp$DERS30[i] + df.temp$DERS31[i] +                                          df.temp$DERS35[i] + df.temp$DERS36[i])
  df.temp$DERS.LackClarity.FU[i] <- sum(df.temp$DERS01[i] + df.temp$DERS04[i] + df.temp$DERS05[i] + df.temp$DERS07[i] + df.temp$DERS09[i])
}
rm(DERS.Reverse)
```

``` {r Scoring IUS-SF}
for (i in 1:length(rownames(df.temp))){
  for (s in 135:146){
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Not at all\ncharacteristic of me\n")
      df.temp[i,s] <- 1
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "A little \ncharacteristic of me\n")
      df.temp[i,s] <- 2
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Somewhat\n\ncharacteristic of me\n")
      df.temp[i,s] <- 3
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Very\ncharacteristic of me\n")
      df.temp[i,s] <- 4
    if (!is.na(df.temp[i,s]) & df.temp[i,s] == "Entirely\ncharacteristic of me\n")
      df.temp[i,s] <- 5
    }
}

for (i in 135:146){
  df.temp[,i] <- as.numeric(df.temp[,i])
}

for (i in 1:length(rownames(df.temp))){
  df.temp$IUS.FU[i] <- sum(df.temp$IUS.SF01[i] + df.temp$IUS.SF02[i] + df.temp$IUS.SF03[i] + df.temp$IUS.SF04[i] + df.temp$IUS.SF05[i] + df.temp$IUS.SF06[i] +
                         df.temp$IUS.SF07[i] + df.temp$IUS.SF08[i] + df.temp$IUS.SF09[i] + df.temp$IUS.SF10[i] + df.temp$IUS.SF11[i] + df.temp$IUS.SF12[i])
  df.temp$IUS_F1.FU[i] <- sum(df.temp$IUS.SF01[i] + df.temp$IUS.SF02[i] + df.temp$IUS.SF04[i] + df.temp$IUS.SF05[i] + df.temp$IUS.SF08[i] + df.temp$IUS.SF09[i] + df.temp$IUS.SF11[i])
  df.temp$IUS_F2.FU[i] <- sum(df.temp$IUS.SF03[i] + df.temp$IUS.SF06[i] + df.temp$IUS.SF07[i] + df.temp$IUS.SF10[i] + df.temp$IUS.SF12[i])
}
rm(i,s)
```

``` {r Losing Scale Responses}
df.temp <- df.temp[,-c(89:146)]
```

# DATAFRAME FORMATTING

I made a mistake in my initial dataframe creation in that I included 6 events which technically did not fit our criteria (i.e., they included only positive emotions and no negative emotions). We'd like to remove those. 

```{r Reformatting Dataframe Into Long Form}
df.temp <-pivot_longer(data=df.temp,
                       cols=colnames(df.temp[1:88]),
                       names_to="Event",
                       values_to="Strategy.FU")
```

```{r Loading dataframe}
  setwd(WorkDir)
  df.og <- read.csv(file = "data/Study_01/Derivative/df_subset.csv", 
                 header = T, sep=",",
                 row.names = 1,
                 stringsAsFactors = F,
                 na.strings=c("","N/A"))
```

```{r Loading dataframe}
  setwd(WorkDir)
  df.og.el <- read.csv(file = "data/Study_01/Derivative/df_subset_eventlevel.csv", 
                 header = T, sep=",",
                 row.names = 1,
                 stringsAsFactors = F,
                 na.strings=c("","N/A"))
```

```{r Creating a person level dataframe for the og dataset}
df.og <- merge(y = df.og.el,
               x = df.og,
               by.y = c("PID", "Event_chronolorder", "IUS_Factor2"),
               by.x = c("PID.OG", "Event_chronolorder", "IUS_F2.OG"),
               all.y = F,
               all.x = T) %>%
               .[,-which(names(.) == "Attention.Deployment")]
```

``` {r Merging Fear Endorsements with the Main Dataframe}
  df <- merge(df.temp, 
              df.og, 
              by = "Event", 
              all.x = F, 
              all.y = T) %>%
        distinct()
  rm(df.temp, df.og, df.og.el)
```

```{r Creating an Accuracy Variable}  
  df$Accurate[df$Strategy.FU == df$Strategy.OG] <- 1
  df$Accurate[df$Strategy.FU != df$Strategy.OG] <- 0
```  

It may be the case that individuals are more accurate and predicting strategy when they have more similar underlying tendencies. As such would be a good control analysis to see whether or not that's the case, and I think the only measure we have of that from both original and follow-up participants is likely the ERQ.

```{r Creating an Accuracy Variable}
  df$ERQ_Reapp.Diff <- df$ERQ_Reapp.FU - df$ERQ_Reapp.OG
  df$ERQ_Supp.Diff <- df$ERQ_Supp.FU - df$ERQ_Supp.OG
  df$ERQ_Reapp.Diff.abs <- abs(df$ERQ_Reapp.Diff)
  df$ERQ_Supp.Diff.abs <- abs(df$ERQ_Supp.Diff)
  df$ERQ_Reapp.Diff.abs.z <- scale(df$ERQ_Reapp.Diff.abs, center = T, scale = T)
  df$ERQ_Supp.Diff.abs.z <- scale(df$ERQ_Supp.Diff.abs, center = T, scale = T)
  names(df) <- str_replace_all(string = names(df),
                               pattern = "\\[\\,1\\]",
                               replacement = "")
  
```  

#  CREATING A PERSON LEVEL DATAFRAME

````{r Designating Rows}
rows <- sort(unique(df$PID.FU))
```

````{r Designating Columns}
cols <- c("PID.FU", "Percent.Distract", "dprime_Distract", "dprime_Reapp", "Accuracy", "ERQ_Reapp.FU")
```

````{r Designating Columns}
df.pl <-data.frame(matrix(NA, 
                   nrow = length(rows), 
                   ncol = length(cols), 
                   dimnames = list(rows, cols)))
rm(cols)
```

```{r Creating a Numeric Strategy Variable to Calculate Stats}
df$Strategy.FU_num <- 0
df$Strategy.FU_num[df$Strategy.FU == "Distraction"] <- 1
```

````{r Populating PID, ERQ, and individual difference measures}
df.pl$PID.FU <- rows
for (i in rows){
  df.pl$Gender[df.pl$PID.FU == i] <- df$Gender.Identity[df$PID.FU == i][1]
  df.pl$Age[df.pl$PID.FU == i] <- df$Age[df$PID.FU == i][1]
  df.pl$ERQ_Reapp.FU[df.pl$PID.FU == i] <- df$ERQ_Reapp.FU[df$PID.FU == i][1]
  df.pl$ERQ_Supp.FU[df.pl$PID.FU == i] <- df$ERQ_Supp.FU[df$PID.FU == i][1]
  df.pl$DERS.FU[df.pl$PID.FU == i] <- df$DERS.FU[df$PID.FU == i][1]
  df.pl$DERS.Nonaccept.FU[df.pl$PID.FU == i] <- df$DERS.Nonaccept.FU[df$PID.FU == i][1]
  df.pl$DERS.DiffGoal.FU[df.pl$PID.FU == i] <- df$DERS.DiffGoal.FU[df$PID.FU == i][1]
  df.pl$DERS.Impulse.FU[df.pl$PID.FU == i] <- df$DERS.Impulse.FU[df$PID.FU == i][1]
  df.pl$DERS.LimitAccess.FU[df.pl$PID.FU == i] <- df$DERS.LimitAccess.FU[df$PID.FU == i][1]
  df.pl$DERS.LackClarity.FU[df.pl$PID.FU == i] <- df$DERS.LackClarity.FU[df$PID.FU == i][1]
  df.pl$IUS.FU[df.pl$PID.FU == i] <- df$IUS.FU[df$PID.FU == i][1]
  df.pl$IUS_F1.FU[df.pl$PID.FU == i] <- df$IUS_F1.FU[df$PID.FU == i][1]
  df.pl$IUS_F2.FU[df.pl$PID.FU == i] <- df$IUS_F2.FU[df$PID.FU == i][1]   
  df.pl$ERQ_Reapp.Diff.abs.avg[df.pl$PID.FU == i] <-mean(df$ERQ_Reapp.Diff.abs[df$PID.FU == i], na.rm= T)
  df.pl$ERQ_Supp.Diff.abs.avg[df.pl$PID.FU == i] <- mean(df$ERQ_Supp.Diff.abs[df$PID.FU == i], na.rm= T)
  df.pl$ERQ_Reapp.Diff.abs.z.avg[df.pl$PID.FU == i] <-mean(df$ERQ_Reapp.Diff.abs.z[df$PID.FU == i], na.rm= T)
  df.pl$ERQ_Supp.Diff.abs.z.avg[df.pl$PID.FU == i] <- mean(df$ERQ_Supp.Diff.abs.z[df$PID.FU == i], na.rm= T)
}
rm(i)
```

```{r Populating accuracy and percentage of distraction}
df_temp <- subset(df,
                  select = c("PID.FU", "Event", "Accurate", "Strategy.FU_num", "Strategy.FU", "Strategy.OG")) %>%
           distinct()

for (i in rows){
  df.pl$Percent.Distract[df.pl$PID.FU == i] <- sum(df_temp$Strategy.FU_num[df_temp$PID.FU == i], na.rm= T)/length(unique(df_temp$Event))
  
  df.pl$Accuracy[df.pl$PID.FU == i] <- sum(df_temp$Accurate[df_temp$PID.FU == i], na.rm= T)/length(unique(df_temp$Event))
  
  #NOTE: D Prime is calculated as the normalized value of the proportion of hits (when the target was present and selected) minus the proportion of false alarms (when the target was absent and selected).
  
  df.pl$dprime_Distract[df.pl$PID.FU == i] <- qnorm(length(which(df_temp$Accurate == 1 &
                                                           df_temp$PID.FU == i & 
                                                           df_temp$Strategy.FU == "Distraction"))/length(unique(df_temp$Event))) -
                                              qnorm(length(which(df_temp$Accurate == 0 &
                                                           df_temp$PID.FU == i &
                                                           df_temp$Strategy.FU == "Distraction"))/length(unique(df_temp$Event)))  
  
  df.pl$dprime_Reapp[df.pl$PID.FU == i] <- qnorm(length(which(df_temp$Accurate == 1 &
                                                        df_temp$PID.FU == i & 
                                                        df_temp$Strategy.FU == "Reappraisal"))/length(unique(df_temp$Event))) -
                                           qnorm(length(which(df_temp$Accurate == 0 &
                                                        df_temp$PID.FU == i &
                                                        df_temp$Strategy.FU == "Reappraisal"))/length(unique(df_temp$Event))) 
}

rm(df_temp,i)
```

# EXPORTING

```{r Writing Data}
write.csv(df, paste0(Export, "df.csv"))
write.csv(df.pl, paste0(Export, "df_personlevel.csv"))
```