---
title: "ER Choice v. Usage - Study 3"
author: "William J. Mitchell"
date: "2021 / 08 / 05"
output: html_document
---

NAVIGATION / QUESTIONS:
+ In previous analyses and reviews of our haunted house data set, we've found that affective intensity predicted regulation extent, but not regulation strategy choice. This is what we expected to find, but it's in contradiction with the vast amount of lab research which finds some massive associations between choice and intensity (on the magnitude of r+ = 0.65 - 0.80). If that were the case, power analyses suggested even 20 people should have been enough to demonstate the relationship. Importantly, we were not decontextualizing or isolating our stimuli of interest, which many lab studies understandly and necessarily do. What we wanted to see with this experiment is whether decontextualizing the experiences of people who previously showed no choice-intensity relationships introduces the lab-supported patterns.

PREDICTIONS:
+ We predict that as affective intensity increases, forecasters, or people who are predicting what they would do in the given situation but had not experienced it, will be more likely to select distraction over reappraisal. We hope that this relationship holds up even after accounting for important individual difference measures like ERQ. 

ISSUES:
+ During initial collection, participants were asked the extent to which they had felt a specific emotion and during the follow up, the emotion ratings the original participants provided were presented as emotional intensity, rather than emotional extent.

NOTES:

# SCRIPT START 

Specifying our package usage
```{r Packages I Use}
   pacman::p_load(effects, 
                  lme4, 
                  performance, 
                  psych, 
                  stargazer, 
                  tidyverse)
```

Indicating how I want numbers presented and formatted
``` {r Number Formatting}
  options(scipen=100)
  options(digits=3)
  options(tinytex.verbose = TRUE)
```
  
Specifying my working directories
```{r Setting Working Directories}
  # Identifying our main directory
  WorkDir <- "C:/Users/wjpmi/Dropbox/My PC (UncleSplashysSaddnessEmporium)/Desktop/Grad School/Projects/Complete/Fright Night/Public_Records/"

  # Identifying specific directories to read and write from
  Export <- paste0(WorkDir, "data/Study_03/Derivative/")
  Import <- paste0(WorkDir, "data/Study_03/Raw/")
  Plots <- paste0(WorkDir, "plots/")
```


## LOADING THE ORIGINAL (EXPERIENCER) DATA 
  
```{r Loading experiencer dataframe}
  setwd(WorkDir)
  df.og <- read.csv(file = "data/Study_01/Derivative/df_subset.csv", 
                    header = T, 
                    sep=",", 
                    stringsAsFactors = F,
                    na.strings=c("","N/A"),
                    row.names = 1)
```


```{R Summaries}
paste("Observations:", nrow(df.og))
paste("Unique Events:", nrow(unique(df.og[,c('PID.OG', 'Event')])))
paste("Average Number of Emotions Per Event:", round(nrow(df.og)/nrow(unique(df.og[,c('PID.OG', 'Event')])),2))
paste("Total Number of Participants:", nrow(distinct(subset(df.og, select = c("PID.OG")))))
paste("Total Number of Reappraisal Events:", nrow(distinct(subset(df.og, df.og$Strategy.OG == "Reappraisal" , select = c("Strategy.OG", "Event")))))
paste("Total Number of Distraction Events:", nrow(distinct(subset(df.og, df.og$Strategy.OG== "Distraction" ,select = c("Strategy.OG", "Event")))))
```

## LOADING THE FOLLOW UP (PREDICTOR) DATA 

```{r Loading standard dataframe}
  setwd(Import)
  df.fu <- read.csv(file = "df.csv", 
                    header = T, 
                    sep=",", 
                    stringsAsFactors = F,
                    na.strings=c("","N/A"),
                    row.names = 1)
```

```{r Loading person level dataframe}
  setwd(Import)
  df.fu.pl <- read.csv(file = "df_personlevel.csv", 
                    header = T, 
                    sep=",", 
                    stringsAsFactors = F,
                    na.strings=c("","N/A"),
                    row.names = 1)
```

# QUALITY ASSURANCE CHECK 

```{r Removing NAs}
df.fu <- subset(df.fu, 
                !is.na(df.fu$PID.FU))
```

Individuals who score high on the DERS 5th subscale may present an issue for our data, so I'd like to assess the prominence of those individuals in the dataset.

```{r Assessing the distributions of emotions}
df.fu.pl$group <- "Participants"
ggplot(data = df.fu.pl, aes(x = group, y = DERS.LimitAccess.FU)) + 
       theme_classic()+
       labs(x ="") +
       geom_jitter(aes(alpha=0.2, color = group),shape=16, position=position_jitter(0.2)) + 
       geom_violin(trim=F, alpha=0.5) +
       scale_color_nord(palette = "afternoon_prarie", discrete = T) +
       ylab("DERS - Limited Access to ER Strategies Subscale") +
       theme(legend.position="none") +
       geom_boxplot(width=0.2, color="black", alpha=0.2)
```

I'm also curious whether these two groups differ significantly from one another in ERQ scores

```{r Creating a person level dataframe for the og dataset}
df.og.pl <- subset(df.og, select= c("PID.OG", "ERQ_Reapp.OG", "ERQ_Supp.OG", "IUS_F2.OG")) %>%
            distinct()
```

```{r Comparing ERQ Reapp}
t.test(x=df.og.pl$ERQ_Reapp.OG, y = df.fu.pl$ERQ_Reapp.FU,alternative = "two.sided",paired = F, var.equal = F)
```

```{r Comparing ERQ Suppress}
t.test(x=df.og.pl$ERQ_Supp.OG, y = df.fu.pl$ERQ_Supp.FU,alternative = "two.sided",paired = F,var.equal = F)
```

```{r Comparing IUS}
t.test(x=df.og.pl$IUS_F2.OG, y = df.fu.pl$IUS_F2.FU,alternative = "two.sided",paired = F,var.equal = F)
```

The two samples do not differ significantly by ERQ Reappraisal scores (xexp = 29.9 xfor= 31.0, t(45) = -1). However, significant differences were observed between the two groups for the expressive suppression ERQ subscale (xexp = 12.5, xfor = 15.7, t(48) = -3, p < 0.001) and the IUS Factor 2 subscale (xexp = 30.4, xfor = 12.6, t(35) = 11, p < 0.001). Though ERQ subscales  demonstrated no significant predictive utility towards regulatory effort in Study 1, IUS Factor 2 demonstrated a negative association with regulation effort (b = -0.052, 95% CI=[-0.080, -0.025], p < 0.001). Neither scale was assocaited with strategy usage in Study 1.  

# AFFECTIVE RESPONSES DID PREDICT STRATEGY PREDICTION  

```{r Restructuing Variables}
df.fu$Strategy.FU <- as.factor(df.fu$Strategy.FU) %>%
                     relevel(ref = "Reappraisal")
df.fu$Age <- as.numeric(df.fu$Age)
df.fu$Gender.Identity <- as.factor(df.fu$Gender.Identity)
df.fu$IUS_F2.FU <- as.numeric(df.fu$IUS_F2.FU)
df.fu$Accurate <- as.numeric(df.fu$Accurate)
df.fu$DERS.LimitAccess.FU <- as.numeric(df.fu$DERS.LimitAccess.FU)
df.fu <- subset(df.fu, !is.na(df.fu$Strategy.FU) &
                        !is.na(df.fu$Age) & 
                        !is.na(df.fu$Gender.Identity) &
                        !is.na(df.fu$IUS_F2.FU))
```

```{r Mixed Effect Logistic Regression Model - NULL}
m0 <- glmer(Strategy.FU ~ 1 + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
icc(m0)
```

```{r Mixed Effect Logistic Regression Model - FIXED EFFECT}
m1 <- glmer(Strategy.FU ~ Emo.Extent.z + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
m2 <- glmer(Strategy.FU ~ Emo.Extent.z + Age + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
m3 <- glmer(Strategy.FU ~ Emo.Extent.z + Gender.Identity + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
m4 <- glmer(Strategy.FU ~ Emo.Extent.z + IUS_F2.FU + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
m5 <- glmer(Strategy.FU ~ Emo.Extent.z + DERS.LimitAccess.FU + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
m6 <- glmer(Strategy.FU ~ Emo.Extent.z + Age + Gender.Identity + IUS_F2.FU + DERS.LimitAccess.FU + (1 | PID.FU) + (1 | PID.OG), data = df.fu, family = binomial)
```

```{r Model Comparisons}  
anova(m0, m1)
anova(m1, m2)
anova(m2, m3)
anova(m3, m4)
anova(m4, m5)
anova(m5, m6)
```

```{r Model Outputs}  
class(m0) <- "lmerMod"
class(m1) <- "lmerMod"
class(m2) <- "lmerMod"
class(m3) <- "lmerMod"
class(m4) <- "lmerMod"
class(m5) <- "lmerMod"
class(m6) <- "lmerMod"
stargazer(m0,m1,m2, m3,m4,m5, m6,
          type = "text", 
          title= "Intensity Predicting Regulation", 
          column.labels = c("Null Model", "Model 1", "Model 2", "Model 3", "Model 4", "Model 5", "Model 6"),
          dep.var.labels = "Strategy Selection", 
          star.cutoffs = c(0.05, 0.01,0.001),
          covariate.labels = c("Affective Intensity (z)", "Age", 
                               "Gender, Male", 
                               "Gender, Non-Binary", 
                               "IUS, Factor 2", 
                               "DERS Limited Access to Strategies", 
                               "Intercept"), ci = T,
          notes = "")
```

```{r Converting Beta to an Odds Ratio}
exp(fixef(m1))
exp(0.017)
exp(0.091)
```

```{r Mixed Effect Logistic Regression Model - FIXED EFFECT}
m1.e <- effect("Emo.Extent.z",m1,xlevels=list(Emo.Extent.z=seq(range(df.fu$Emo.Extent.z)[1],
                                                       range(df.fu$Emo.Extent.z)[2],
                                                       0.01))) 
m1.e <-as.data.frame(m1.e)
head(m1.e)
plot <- ggplot(m1.e, aes(x=Emo.Extent.z, y=fit)) +
  geom_jitter(data = df.fu, aes(x=Emo.Extent.z, y=Strategy.FU_num, color=Strategy.FU_num), size = 0.1, alpha = 0.1, width = 0.5, height = 0.025) +
  geom_line(color = "Black", size = 1.5) +
  geom_ribbon(aes(ymin=lower, ymax=upper), alpha = 0.15) +
  labs(title = "Emotion Intensity Predicts Strategy Choice",
       subtitle = ("OR = 1.056 **")) +
  scale_x_continuous("Emotion Intensity (z)", breaks = round(seq(range(df.fu$Emo.Extent.z)[1],
                                                         range(df.fu$Emo.Extent.z)[2], 
                                                         (range(df.fu$Emo.Extent.z)[2] - range(df.fu$Emo.Extent.z)[1])/6),0)) +
  scale_y_continuous("Probability of Choosing Strategy", breaks = seq(0,1,0.2), labels = c("Reappraisal","0.2","0.4","0.6","0.8", "Distraction")) +
  coord_cartesian(xlim = c(range(df.fu$Emo.Extent.z)[1],
                           range(df.fu$Emo.Extent.z)[2]), ylim = c(0,1)) +
  theme_classic() +  
  theme(legend.position = "none") +
  theme(plot.title = element_text(face="bold", size=8, hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 8, hjust = 0.5, face = "italic")) +
  theme(plot.caption = element_text(size = 4, hjust = 0.00, face = "italic")) +
  theme(axis.title = element_text(size = 10)) +
  theme(axis.text.x = element_text(size = 10, color = "Black")) +
  theme(axis.text.y = element_text(size = 10, color = "Black")) 
plot
```

```{r Exporting Regulation & Intensity Regression}
  setwd(Plots)
  pdf("FN02_EmoExtent_Strategy.pdf",
      width = 4, 
      height = 3)
  plot
  dev.off()
  rm(plot, m0, m1, m2, m3, m1.e)
```

# AFFECTIVE RESPONSES DID PREDICT STRATEGY PREDICTION AT EVENT LEVEL (MEAN)

```{r Subsetting event level data}
df_temp <- df.fu %>%
           .[,-which(names(.) %in% c("Emotion", "Emo.Extent", "Emo.Extent.z",
                                     "Reg.Extent", "Reg.Extent.z"))] %>%
           distinct()
```

```{r Mixed Effect Logistic Regression Model - NULL}
m0 <- glmer(Strategy.FU ~ 1 + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
icc(m0)
```

```{r Mixed Effect Logistic Regression Model - FIXED EFFECT}
m1 <- glmer(Strategy.FU ~ Emo_Mean.z + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m2 <- glmer(Strategy.FU ~ Emo_Mean.z + Age + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m3 <- glmer(Strategy.FU ~ Emo_Mean.z + Gender.Identity + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m4 <- glmer(Strategy.FU ~ Emo_Mean.z + IUS_F2.FU + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m5 <- glmer(Strategy.FU ~ Emo_Mean.z + DERS.LimitAccess.FU + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m6 <- glmer(Strategy.FU ~ Emo_Mean.z + Age + Gender.Identity + IUS_F2.FU + DERS.LimitAccess.FU + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
```

```{r Model Comparisons}  
anova(m0, m1)
anova(m1, m2)
anova(m2, m3)
anova(m3, m4)
anova(m4, m5)
anova(m5, m6)
```

```{r Model Outputs}  
class(m0) <- "lmerMod"
class(m1) <- "lmerMod"
class(m2) <- "lmerMod"
class(m3) <- "lmerMod"
class(m4) <- "lmerMod"
class(m5) <- "lmerMod"
class(m6) <- "lmerMod"
stargazer(m0,m1,m2, m3,m4,m5, m6,
          type = "text", 
          title= "Intensity Predicting Regulation", 
          column.labels = c("Null Model", "Model 1", "Model 2", "Model 3", "Model 4", "Model 5", "Model 6"),
          dep.var.labels = "Strategy Selection", 
          star.cutoffs = c(0.05, 0.01,0.001),
          covariate.labels = c("Affective Intensity (z)", "Age",                                      "Gender, Male", "Gender, Non-Binary", "IUS, Factor 2", "DERS Limited Access to Strategies", "Intercept"), ci = T,
          notes = "")
```

```{r Converting Beta to an Odds Ratio}
exp(fixef(m1))
exp(0.061)
exp(0.171)
```

```{r Mixed Effect Logistic Regression Model - FIXED EFFECT}
m1.e <- effect("Emo_Mean.z",m1,xlevels=list(Emo_Mean.z=seq(range(df_temp$Emo_Mean.z)[1],
                                                       range(df_temp$Emo_Mean.z)[2],
                                                       0.01))) 
m1.e <-as.data.frame(m1.e)
head(m1.e)
plot <- ggplot(m1.e, aes(x=Emo_Mean.z, y=fit)) +
  geom_jitter(data = df_temp, aes(x=Emo_Mean.z, y=Strategy.FU_num, color=Strategy.FU_num), size = 0.1, alpha = 0.1, width = 0.5, height = 0.025) +
  geom_line(color = "Black", size = 1.5) +
  geom_ribbon(aes(ymin=lower, ymax=upper), alpha = 0.15) +
  labs(title = "Emotion Intensity Predicts Strategy Choice",
       subtitle = ("OR = 1.123 **")) +
  scale_x_continuous("Emotion Intensity (event average, z)", breaks = round(seq(range(df_temp$Emo_Mean.z)[1],
                                                         range(df_temp$Emo_Mean.z)[2], 
                                                         (range(df_temp$Emo_Mean.z)[2] - range(df_temp$Emo_Mean.z)[1])/6),0)) +
  scale_y_continuous("Probability of Choosing Strategy", breaks = seq(0,1,0.2), labels = c("Reappraisal","0.2","0.4","0.6","0.8", "Distraction")) +
  coord_cartesian(xlim = c(range(df_temp$Emo_Mean.z)[1],
                           range(df_temp$Emo_Mean.z)[2]), ylim = c(0,1)) +
  theme_classic() +  
  theme(legend.position = "none") +
  theme(plot.title = element_text(face="bold", size=8, hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 8, hjust = 0.5, face = "italic")) +
  theme(plot.caption = element_text(size = 4, hjust = 0.00, face = "italic")) +
  theme(axis.title = element_text(size = 10)) +
  theme(axis.text.x = element_text(size = 10, color = "Black")) +
  theme(axis.text.y = element_text(size = 10, color = "Black")) 
plot
```

```{r Exporting Regulation & Intensity Regression}
  setwd(Plots)
  pdf("FN02_EmoMean_Strategy.pdf",
      width = 4, 
      height = 3)
  plot
  dev.off()
  rm(plot, m1,m1.e,m2,m3)
```


# AFFECTIVE RESPONSES DID PREDICT STRATEGY PREDICTION AT EVENT LEVEL (SUM)

```{r Mixed Effect Logistic Regression Model - FIXED EFFECT}
m1 <- glmer(Strategy.FU ~ Emo_Sum.z + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m2 <- glmer(Strategy.FU ~ Emo_Sum.z + Age + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m3 <- glmer(Strategy.FU ~ Emo_Sum.z + Gender.Identity + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m4 <- glmer(Strategy.FU ~ Emo_Sum.z + IUS_F2.FU + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m5 <- glmer(Strategy.FU ~ Emo_Sum.z + DERS.LimitAccess.FU + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
m6 <- glmer(Strategy.FU ~ Emo_Sum.z + Age + Gender.Identity + IUS_F2.FU + DERS.LimitAccess.FU + (1 | PID.FU) + (1 | PID.OG), data = df_temp, family = binomial)
```

```{r Model Comparisons}  
anova(m0, m1)
anova(m1, m2)
anova(m2, m3)
anova(m3, m4)
anova(m4, m5)
anova(m5, m6)
```

```{r Model Outputs}  
class(m0) <- "lmerMod"
class(m1) <- "lmerMod"
class(m2) <- "lmerMod"
class(m3) <- "lmerMod"
class(m4) <- "lmerMod"
class(m5) <- "lmerMod"
class(m6) <- "lmerMod"
stargazer(m0,m1,m2, m3,m4, m5, m6,
          type = "text", 
          title= "Intensity Predicting Regulation", 
          column.labels = c("Null Model", "Model 1", "Model 2", "Model 3", "Model 4", "Model 5", "Model 6"),
          dep.var.labels = "Strategy Selection", 
          star.cutoffs = c(0.05, 0.01,0.001),
          covariate.labels = c("Affective Intensity (z)",  
                               "Age",                                      
                               "Gender, Male", 
                               "Gender, Non-Binary", 
                               "IUS, Factor 2", 
                               "DERS Limited Access to Strategies", 
                               "Intercept"), ci = T,
          notes = "")
```

```{r Converting Beta to an Odds Ratio}
exp(fixef(m1))
exp(0.008)
exp(0.049)
```

```{r Mixed Effect Logistic Regression Model}
m1.e <- effect("Emo_Sum.z",m1,xlevels=list(Emo_Sum.z=seq(range(df_temp$Emo_Sum.z)[1],
                                                       range(df_temp$Emo_Sum.z)[2],
                                                       0.01))) 
m1.e <-as.data.frame(m1.e)
head(m1.e)
plot <- ggplot(m1.e, aes(x=Emo_Sum.z, y=fit)) +
  geom_jitter(data = df_temp, aes(x=Emo_Sum.z, y=Strategy.FU_num, color=Strategy.FU_num), size = 0.1, alpha = 0.1, width = 0.5, height = 0.025) +
  geom_line(color = "Black", size = 1.5) +
  geom_ribbon(aes(ymin=lower, ymax=upper), alpha = 0.15) +
  labs(title = "Emotion Intensity Predicts Strategy Choice",
       subtitle = ("OR = 1.029 **")) +
  scale_x_continuous("Emotion Intensity (event sum, z)", breaks = round(seq(range(df_temp$Emo_Sum.z)[1],
                                                         range(df_temp$Emo_Sum.z)[2], 
                                                         (range(df_temp$Emo_Sum.z)[2] - range(df_temp$Emo_Sum.z)[1])/10),0)) +
  scale_y_continuous("Probability of Choosing Strategy", breaks = seq(0,1,0.2), labels = c("Reappraisal","0.2","0.4","0.6","0.8", "Distraction")) +
  coord_cartesian(xlim = c(range(df_temp$Emo_Sum.z)[1],
                           range(df_temp$Emo_Sum.z)[2]), ylim = c(0,1)) +
  theme_classic() +  
  theme(legend.position = "none") +
  theme(plot.title = element_text(face="bold", size=8, hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 8, hjust = 0.5, face = "italic")) +
  theme(plot.caption = element_text(size = 4, hjust = 0.00, face = "italic")) +
  theme(axis.title = element_text(size = 10)) +
  theme(axis.text.x = element_text(size = 10, color = "Black")) +
  theme(axis.text.y = element_text(size = 10, color = "Black")) 
plot
```

```{r Exporting Regulation & Intensity Regression}
  setwd(Plots)
  pdf("FN02_EmoSum_Strategy.pdf",
      width = 4, 
      height = 3)
  plot
  dev.off()
  rm(plot, m0,m1,m1.e,m2,m3,m4,m5,m6,df_temp,df.fu,df.fu.pl,df.og,df.og.pl)
```