---
  title: "ER Forecast v. Usage - Study 3 Dataframe Creation"
author: "W.J. Mitchell"
date: "`r Sys.Date()`"
output: html_document
---

NAVIGATION / QUESTIONS: 
+ Studies 01 and 02 found a different pattern of results for experiencers and forecasts, but there were many differences between the studies. Study 03 is attempting to put them on the same plane and see what differences emerge. We were unable to use an immersive, dynamic setting like in Study 01, but we at least use dynamic, multimodal stimuli - horror videos. By manipulating condition and intensity, we can explore differences in how participants regulate and plan to regulate in response to varying intensity stimuli.

NOTES: 
Because the raw Pavlovia data contains Prolific IDs, which can be identifying, access to this data will not be made public. If you have any questions, please don't hesitate to contact me at *billy.mitchell@temple.edu*. 

```{r pavlovia_cleaner || v2023.10.14}
pavlovia_cleaner <- function(file) {

  # ----- Packages -----
  
  ## Loading packages
  if (require("pacman") == FALSE){
    install.packages("pacman")
  }
  
  ## Loading in my packages with my pacman manager
  pacman::p_load(assertthat, here, jsonlite, tidyverse)
  
  # ----- QA Checks ----- 

  if (!is.string(file)){
    stop(paste("file refers to the raw file generated by Pavlovia in .csv format. It must be valid string, but your entry (",
               file, ") is not a string. Please enter a string and try again."))
  }
  
  if (!str_detect(file, "\\.csv")){
    stop(paste("file refers to the raw file generated by Pavlovia in .csv format. It must be valid .csv file, but your entry does not include a .csv file name (",
               file, "). Please enter a file name with a valid .csv extension and try again."))
  }
  
  if (!file.exists(file)){
    stop(paste("file refers to the raw file generated by Pavlovia in .csv format. It must be valid filepath, but no file exists at your entry (",
               file, "). Please enter a valid file path and try again."))
  }
  
  # ----- Setup -----
  
  ## Creating a general dataframe
  df <- read.csv(file,
              na.strings = c(" ", ""))
  
  ## If no tasks occurred ...
  if (all(names(df) != "task")){
    stop(paste("No usable data was found for datafile: ", file, ". Processing of this file has been terminated."))
  }
  
  ## If no videos were shown ...
  if (all(df$task != "Stimulus")){
    stop(paste("No video trials were found for datafile: ", file, ". Processing of this file has been terminated."))
  }
  
  # ----- Cleaning Observation Data -----
  
  ## Creating a dataframe of trial by trial observations
  df_observ <- df %>%
            subset(select = c("task", "time_elapsed", "rt", 
                     "stimulus", "response", "choices"))
  
  ## Creating a new trial-level dataframe
  df_trials <- data.frame(Trial = 1:length(which(df_observ$task == "Stimulus")))
  
  ## If any videos were shown ...
  if (any(df_observ$task == "Stimulus")){
    
    ## Extracting Stimulus Information
    df_trials$Stimulus <- df_observ$stimulus[df_observ$task == "Stimulus" & !is.na(df_observ$task)] %>%
                          gsub('.*/(\\w+)\\.mp4.*', '\\1',
                               x = .)
  }
    
  ## Extracting Choice Information
  Choice_Order <- df_observ$choices[df_observ$task == "Strategy_Choice" & !is.na(df_observ$task)][1] %>%
                  gsub("\\\\", "", .) %>%
                  regmatches(., gregexpr('(?<=">)[^<]+', ., perl=TRUE)) %>%
                  unlist()
  
  df_trials$Choice <- df_observ$response[df_observ$task == "Strategy_Choice" & !is.na(df_observ$task)] %>%
                      as.numeric() %>%
                      sapply(., function(x) x + 1) %>%
                      Choice_Order[.]
  
  ## Extracting Choice Response Time
  df_trials$RT_sec_Choice <- as.numeric(df_observ$rt[df_observ$task == "Strategy_Choice" & !is.na(df_observ$task)])/1000
  
  ## Extracting Reported Intensity Before
  df_trials$IntBefore <- df_observ$response[df_observ$task == "Intensity_Baseline" & !is.na(df_observ$task)]
  
  ## Extracting Baseline Intensity Response Time
  df_trials$RT_sec_IntBefore <- as.numeric(df_observ$rt[df_observ$task == "Intensity_Baseline" & !is.na(df_observ$task)])/1000
  
  ## Extracting Reported Intensity After
  df_trials$IntAfter <- df_observ$response[df_observ$task == "Intensity_Video" & !is.na(df_observ$task)]
  
  ## Extracting Post Exposure Intensity Response Time
  df_trials$RT_sec_IntAfter <- as.numeric(df_observ$rt[df_observ$task == "Intensity_Video" & !is.na(df_observ$task)])/1000
  
  ## If no regulation strategy was chosen
  if (!all(df_trials$Choice == "Neither")){
    
    ## Extracting Reported Intensity Reduction
    df_trials$IntReduce[df_trials$Choice != "Neither"] <- df_observ$response[df_observ$task == "Intensity_Reduction" & !is.na(df_observ$task)]
    
    ## Extracting Intensity Reduction Response Time
    df_trials$RT_sec_IntReduce[df_trials$Choice != "Neither"] <- as.numeric(df_observ$rt[df_observ$task == "Intensity_Reduction" & !is.na(df_observ$task)])/1000
    
    ## Extracting Reported Effort
    df_trials$Effort[df_trials$Choice != "Neither"] <- df_observ$response[df_observ$task == "Effort" & !is.na(df_observ$task)] %>%
                                                       gsub("[^0-9.]", "", .) %>%
                                                       as.numeric()
    
    ## Extracting Effort Response Time
    df_trials$RT_sec_Effort[df_trials$Choice != "Neither"] <- as.numeric(df_observ$rt[df_observ$task == "Effort" & !is.na(df_observ$task)])/1000
    
    ## Extracting Reported Success
    df_trials$Success[df_trials$Choice != "Neither"] <- df_observ$response[df_observ$task == "Success" & !is.na(df_observ$task)] %>%
                                                        gsub("[^0-9.]", "", .) %>%
                                                        as.numeric()
    
    ## Extracting Success Response Time
    df_trials$RT_sec_Success[df_trials$Choice != "Neither"] <- as.numeric(df_observ$rt[df_observ$task == "Success" & !is.na(df_observ$task)])/1000
    
  }
  
  rm(df_observ, Choice_Order)
  
  # ----- Cleaning Scale Data ------
  
  if (any(df$task[!is.na(df$task)] == "Scale")){
    
    ## Creating a dataframe of scale responses
    df_scale <- df[df$task == "Scale" & !is.na(df$task),] %>%
      subset(select = c("trial_index", "time_elapsed", "rt", "response", "question_order"))
    
    ## Extracting ERQ Column Names
    ERQ_cols <- strsplit(df_scale$response[grepl("ERQ", df_scale$response)], ",") %>%
      unlist() %>%
      gsub('.*"(ERQ_\\d+)".*', '\\1', .)
    
    ## Extracting ERQ Values
    ERQ_vals <- strsplit(df_scale$response[grepl("ERQ", df_scale$response)], ",") %>%
      unlist() %>%
      gsub('.*:(\\d+).*', '\\1', .)
    
    ## Extracting IUS Column Names
    IUS_cols <- strsplit(df_scale$response[grepl("IUS", df_scale$response)], ",") %>%
      unlist() %>%
      gsub('.*"(IUS-SF_\\d+)".*', '\\1', .)
    
    ## Extracting IUS Values
    IUS_vals <- strsplit(df_scale$response[grepl("IUS", df_scale$response)], ",") %>%
      unlist() %>%
      gsub('.*:(\\d+).*', '\\1', .)
    
    ## Extracting DERS Column Names
    DERS_cols <- strsplit(df_scale$response[grepl("DERS", df_scale$response)], ",") %>%
      unlist() %>%
      gsub('.*"(DERS_\\d+)".*', '\\1', .)
    
    ## Extracting DERS Values
    DERS_vals <- strsplit(df_scale$response[grepl("DERS", df_scale$response)], ",") %>%
      unlist() %>%
      gsub('.*:(\\d+).*', '\\1', .)
    
    ## Creating arrays of Questions and Values
    Scale_Question <- c(ERQ_cols, DERS_cols, IUS_cols)
    Scale_Value <- c(ERQ_vals, DERS_vals, IUS_vals)
    
    ## Capturing how long scales took to complete
    Scale_RT_sec <- as.numeric(df_scale$rt)/1000
    Scale_RT_sec <- c(rep(Scale_RT_sec[1], length(ERQ_cols)),
                      rep(Scale_RT_sec[2], length(DERS_cols)),
                      rep(Scale_RT_sec[3], length(IUS_cols)))
    
    ## Creating a dataframe
    df_scale <- data.frame(Scale_Question,
                           Scale_Value,
                           Scale_RT_sec)
    
    ## Cleaning our space
    rm(ERQ_cols, DERS_cols, IUS_cols, ERQ_vals, DERS_vals, IUS_vals, Scale_Question, Scale_Value, Scale_RT_sec)
    
    ## Calculating ERQ Summary Scores
    ## Calculating the suppression subscale
    df_trials$ERQ_Supp <- which(df_scale$Scale_Question %in% c("ERQ_02", "ERQ_04", "ERQ_06", "ERQ_09")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    ## Calculating the reappraisal subscale
    df_trials$ERQ_Reapp <- which(df_scale$Scale_Question %in% c("ERQ_01", "ERQ_03", "ERQ_05", "ERQ_07", "ERQ_08", "ERQ_10")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$RT_sec_ERQ <- df_scale$Scale_RT_sec[df_scale$Scale_Question == "ERQ_01"]
    
    ## Calculating DERS Summary Scores
    ## Reverse Scoring Specific Cases
    for (VALUE in c("DERS_01", "DERS_02", "DERS_06", "DERS_07", 
                    "DERS_08", "DERS_10", "DERS_17", "DERS_20", 
                    "DERS_22", "DERS_24", "DERS_34")){
      df_scale$Scale_Value[df_scale$Scale_Question == VALUE] <- 6 - as.numeric(df_scale$Scale_Value[df_scale$Scale_Question == VALUE])
    }
    
    df_trials$DERS <- grepl("^DERS_", df_scale$Scale_Question) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$DERS_Nonaccept <- which(df_scale$Scale_Question %in% c("DERS_11", "DERS_12", "DERS_21", "DERS_23", "DERS_25", "DERS_29")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$DERS_Goals <-  which(df_scale$Scale_Question %in% c("DERS_13", "DERS_18", "DERS_20", "DERS_26", "DERS_33"))%>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$DERS_Impulse <-  which(df_scale$Scale_Question %in% c("DERS_03", "DERS_14", "DERS_19", "DERS_24", "DERS_27", "DERS_32"))%>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$DERS_Awareness <- which(df_scale$Scale_Question %in% c("DERS_02", "DERS_06", "DERS_08", "DERS_10", "DERS_17", "DERS_34")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$DERS_Strategies <- which(df_scale$Scale_Question %in% c("DERS_15", "DERS_16", "DERS_22", "DERS_28", "DERS_30", "DERS_31", "DERS_35", "DERS_36")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$DERS_Clarity <- which(df_scale$Scale_Question %in% c("DERS_01", "DERS_04", "DERS_05", "DERS_07", "DERS_09")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    ## Calculating Time to complete
    df_trials$RT_sec_DERS <- df_scale$Scale_RT_sec[df_scale$Scale_Question == "DERS_01"]
    
    ## Calculating IUS Summary Scores
    df_trials$IUS <- grepl("^IUS-SF_", df_scale$Scale_Question) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    ## Calculating the subscales
    df_trials$IUS_F1 <- which(df_scale$Scale_Question %in% c("IUS-SF_01", "IUS-SF_02", "IUS-SF_04", "IUS-SF_05", "IUS-SF_08", "IUS-SF_09", "IUS-SF_11")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    df_trials$IUS_F2 <- which(df_scale$Scale_Question %in% c("IUS-SF_03", "IUS-SF_06", "IUS-SF_07", "IUS-SF_10", "IUS-SF_12")) %>%
      df_scale$Scale_Value[.] %>%
      as.numeric() %>%
      sum()
    
    ## Calculating Time to complete
    df_trials$RT_sec_IUS <- df_scale$Scale_RT_sec[df_scale$Scale_Question == "IUS-SF_01"]
    
    ## Checking if we have demographics information
    if (any(df$task == "Demographics" & !is.na(df$task))){
     
      ## Working on Demographics
      df_demo <- df$response[df$task == "Demographics" & !is.na(df$task)] %>%
                    fromJSON() %>%
                    as.data.frame()
      
      ## If the one of the demographics has multiple entries
      if (nrow(df_demo) > 1) {
        
        ## We'll iterate throuhg each column
        for (COL in 1:ncol(df_demo)){
          
          ## and find all cases where we have multiple different values
          if (!all(df_demo[,COL] == df_demo[1,COL])){
            
            ## Then we'll copy all of those valuse to our first row
            df_demo[1,COL] <- paste(df_demo[,COL],sep = " / ", collapse = " ")
          }
        }
      }
      
      ## and merge it with the preexisting dataframe
      df_trials <- df_demo[1,] %>%
                   cbind(df_trials, .)
      
    }
    
    ## Cleaning our space
    rm(df_scale, VALUE, df_demo)
  }
  
  # ----- Cleaning Session Data -----
  
  ## Creating a dataframe of variables that should be consistent across the session
  df_session_orig <- df %>%
                subset(select = c("subject_id","success", "time",  "timeout", "failed_images", "failed_audio", 
                                  "failed_video", "width", "height", "webaudio", "browser",
                                  "browser_version", "mobile", "os", "fullscreen", "vsync_rate", "condition")) %>%
                .[rowSums(is.na(.)) != ncol(.), ]
  
  cols_session <- c("PID", "Date", "Start_Time", "End_Time", "Condition", "Failures", "ScreenWidth", "ScreenHeight", "WebAudio",
                    "Browser", "Browser_Version", "MobileUsed", "OS", "FullScreenUsed",
                    "VSync_Rate_Avg", "VSync_Rate_SD", "Horror_Enjoy", "Familiarity", "Familiar_specific",
                    "Attention_Check", "Difficulties", "Questions")
  
  df_session <- as.data.frame(matrix(data = NA, 
                                     nrow = 1,
                                     ncol = length(cols_session),
                                     dimnames = list(1,
                                                     cols_session)))
  
  ## Extracting PID
  df_session$PID <- df$subject_id[1] %>%
                    gsub("[^[:alnum:]]", "", .)
  
  ## Extracting Start Time & End Time
  df_session$Start_Time <- df$time[df$trial_type == "fullscreen" & !is.na(df$trial_type)][1]
  df_session$End_Time <- df$time[df$trial_type == "fullscreen" & !is.na(df$trial_type)][2]
  df_session$Date <- file %>% 
                     regmatches(., regexpr("\\d{4}-\\d{2}-\\d{2}", .))
  
  ## Extracting Condition Information
  if (any(df_session_orig$condition[which(!is.na(df_session_orig$condition))] == "Forecast")) {
    df_session$Condition <- "Strategy Forecast"    
  }
  if (any(df_session_orig$condition[which(!is.na(df_session_orig$condition))] == "Experience")) {
    df_session$Condition <- "Strategy Use"    
  }
  
  ## Checking Event Failures
  if (any(df_session_orig$success[!is.na(df_session_orig$success)] == 'false')) {
    warning(paste("At least one event of file ", file, " has recorded an initialization failure. 
                  Please review this file before continuing."))
    df_session$Failures[1] = TRUE
  }
  if (all(df_session_orig$success[!is.na(df_session_orig$success)] == 'true')) {
    df_session$Failures[1] = FALSE    
  }
  
  ## Checking Screen Width
  if (all(df_session_orig$width[which(!is.na(df_session_orig$width))] != df_session_orig$width[which(!is.na(df_session_orig$width))[1]])) {
    warning(paste("At least one event of file ", file, " has recorded a screen width which differs from the others (", df_session_orig$width[which(!is.na(df_session_orig$width))[1]],") . 
                  Please review this file before continuing."))
    df_session$ScreenWidth[1] = NA
  }
  if (all(df_session_orig$width[which(!is.na(df_session_orig$width))] == df_session_orig$width[which(!is.na(df_session_orig$width))[1]])) {
    df_session$ScreenWidth[1] = df_session_orig$width[which(!is.na(df_session_orig$width))[1]]
  }
  
  ## Checking Screen Height
  if (all(df_session_orig$height[which(!is.na(df_session_orig$height))] != df_session_orig$height[which(!is.na(df_session_orig$height))[1]])) {
    warning(paste("At least one event of file ", file, " has recorded a screen height which differs from the others (", df_session_orig$height[which(!is.na(df_session_orig$height))[1]],") . 
                  Please review this file before continuing."))
    df_session$ScreenHeight[1] = NA
  }
  if (all(df_session_orig$height[which(!is.na(df_session_orig$height))] == df_session_orig$height[which(!is.na(df_session_orig$height))[1]])) {
    df_session$ScreenHeight[1] = df_session_orig$height[which(!is.na(df_session_orig$height))[1]]
  }
  
  ## Checking if webaudio is ever not playing
  if (any(df_session_orig$webaudio[!is.na(df_session_orig$webaudio)] == 'false')) {
    warning(paste("At least one event of file ", file, " has recorded that audio did not initialize. 
                  Please review this file before continuing."))
    df_session$WebAudio[1] = FALSE
  }
  if (all(df_session_orig$webaudio[!is.na(df_session_orig$webaudio)] == 'true')) {
    df_session$WebAudio[1] = TRUE    
  }
  
  ## Checking if mobile is ever recorded
  if (any(df_session_orig$mobile[!is.na(df_session_orig$mobile)] == 'true')) {
    warning(paste("At least one event of file ", file, " has recorded that mobile was used to complete the task. 
                  Please review this file before continuing."))
    df_session$MobileUsed[1] = TRUE
  }
  if (all(df_session_orig$mobile[!is.na(df_session_orig$mobile)] == 'false')) {
    df_session$MobileUsed[1] = FALSE    
  }
  
  ## Checking if fullscreen is ever not used
  if (any(df_session_orig$fullscreen[!is.na(df_session_orig$fullscreen)] == 'false')) {
    warning(paste("At least one event of file ", file, " has recorded that full screen was not used to complete the task. 
                  Please review this file before continuing."))
    df_session$FullScreenUsed[1] = FALSE
  }
  if (all(df_session_orig$fullscreen[!is.na(df_session_orig$fullscreen)] == 'true')) {
    df_session$FullScreenUsed[1] = TRUE
  }

  ## Calculating Average and Standard Deviation of VSync
  df_session$VSync_Rate_Avg <- mean(df_session_orig$vsync_rate, na.rm = T)
  df_session$VSync_Rate_SD <- sd(df_session_orig$vsync_rate, na.rm = T)
  
  ## Copying browser and OS information
  df_session$Browser <- df_session_orig$browser[which(!is.na(df_session_orig$browser))[1]] 
  df_session$Browser_Version <- df_session_orig$browser_version[which(!is.na(df_session_orig$browser_version))[1]] 
  df_session$OS <- df_session_orig$os[which(!is.na(df_session_orig$os))[1]] 
  
  ## If any of the MISC events were captured 
  if (any(str_detect(string = df$task[!is.na(df$task)], pattern = "^Misc"))){
   
    ## Copying other information
    df_session$Horror_Enjoy <- df$response[df$task == "Misc_Horror_Enjoy" & !is.na(df$task)] %>%
      gsub("[^0-9.]", "", .) %>%
      as.numeric()
    
    df_session$Attention_Check <- df$response[df$task == "Misc_Attention_Check" & !is.na(df$task)] %>%
      gsub("[^0-9.]", "", .) %>%
      as.numeric()
    
    df_session$Difficulties <- df$response[df$task == "Misc_Difficulties" & !is.na(df$task)] %>%
      str_match(pattern = '"Q0":"(.*?)"') %>%
      .[2]
    
    df_session$Questions <- df$response[df$task == "Misc_Questions" & !is.na(df$task)] %>%
      str_match(pattern = '"Q0":"(.*?)"') %>%
      .[2]
    if (df$response[df$task == "Misc_Familiar_Any" & !is.na(df$task)] == 1){
      df_session$Familiarity <- "No"
    }
    if (df$response[df$task == "Misc_Familiar_Any" & !is.na(df$task)] != 1){
      df_session$Familiarity <- "Yes"
    }
    if (any(df$task[!is.na(df$task)] == "Misc_Familiar_Specific")){
      df_session$Familiar_specific <- df$response[df$task == "Misc_Familiar_Specific" & !is.na(df$task)] %>%
                                      fromJSON() %>%
                                      as.data.frame() %>%
                                      .[,1] %>%
                                      str_replace_all(pattern = "components/screenshots/",
                                                      replacement = "") %>%
                                      str_replace_all(pattern = "\\.png",
                                                      replacement = "") %>%
                                      paste(., collapse = " ")
                                      
    }
     
  }
  
  # ----- Merging Dataframes -----
  
  ## Merging Dataframes
  df <- cbind(df_trials, df_session)
  
  ## Cleaning space
  rm(df_session, df_trials, cols_session)
  
  # ----- Rearranging Variable Names -----
  
  if (any(names(df) == "ERQ_Supp")){
    if (any(names(df) == "Income")) {
      if (all(df$Choice == "Neither")){
        df <- subset(df,
                     select=c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                              "IntBefore", "IntAfter", "ERQ_Supp", "ERQ_Reapp",
                              "DERS", "DERS_Nonaccept", "DERS_Goals", "DERS_Impulse", "DERS_Awareness", "DERS_Strategies",
                              "DERS_Clarity", "IUS", "IUS_F1", "IUS_F2", "Horror_Enjoy", "Familiarity", "Familiar_specific",
                              "Age", "Gender_Identity", "Sex", "Race", "Marital_Status", "Edu_Num", "Edu_Cat", "Income", "Failures",
                              "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                              "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                              "Attention_Check", "Difficulties", "Questions", "RT_sec_Choice", "RT_sec_IntBefore",
                              "RT_sec_IntAfter", "RT_sec_ERQ", "RT_sec_DERS", "RT_sec_IUS"))
      }
      if (any(df$Choice != "Neither")){
        df <- subset(df,
                     select=c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                              "IntBefore", "IntAfter", "IntReduce", "Effort", "Success", "ERQ_Supp", "ERQ_Reapp",
                              "DERS", "DERS_Nonaccept", "DERS_Goals", "DERS_Impulse", "DERS_Awareness", "DERS_Strategies",
                              "DERS_Clarity", "IUS", "IUS_F1", "IUS_F2", "Horror_Enjoy", "Familiarity", "Familiar_specific",
                              "Age", "Gender_Identity", "Sex", "Race", "Marital_Status", "Edu_Num", "Edu_Cat", "Income", "Failures",
                              "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                              "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                              "Attention_Check", "Difficulties", "Questions", "RT_sec_Choice", "RT_sec_IntBefore",
                              "RT_sec_IntAfter", "RT_sec_IntReduce", "RT_sec_Effort",
                              "RT_sec_Success", "RT_sec_ERQ", "RT_sec_DERS", "RT_sec_IUS"))
      }
    }
    
    if (all(names(df) != "Income")) {
      if (all(df$Choice == "Neither")){
        df <- subset(df,
                     select = c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                                "IntBefore", "IntAfter", "ERQ_Supp", "ERQ_Reapp",
                                "DERS", "DERS_Nonaccept", "DERS_Goals", "DERS_Impulse", "DERS_Awareness", "DERS_Strategies",
                                "DERS_Clarity", "IUS", "IUS_F1", "IUS_F2", "Horror_Enjoy", "Familiarity", "Familiar_specific",
                                "Age", "Gender_Identity", "Sex", "Race", "Marital_Status", "Edu_Num", "Edu_Cat", "Failures",
                                "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                                "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                                "Attention_Check", "Difficulties", "Questions", "RT_sec_Choice", "RT_sec_IntBefore",
                                "RT_sec_IntAfter", "RT_sec_ERQ", "RT_sec_DERS", "RT_sec_IUS"))
      }
      if (any(df$Choice != "Neither")){
        df <- subset(df,
                     select = c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                                "IntBefore", "IntAfter", "IntReduce", "Effort", "Success", "ERQ_Supp", "ERQ_Reapp",
                                "DERS", "DERS_Nonaccept", "DERS_Goals", "DERS_Impulse", "DERS_Awareness", "DERS_Strategies",
                                "DERS_Clarity", "IUS", "IUS_F1", "IUS_F2", "Horror_Enjoy", "Familiarity", "Familiar_specific",
                                "Age", "Gender_Identity", "Sex", "Race", "Marital_Status", "Edu_Num", "Edu_Cat", "Failures",
                                "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                                "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                                "Attention_Check", "Difficulties", "Questions", "RT_sec_Choice", "RT_sec_IntBefore",
                                "RT_sec_IntAfter", "RT_sec_IntReduce", "RT_sec_Effort",
                                "RT_sec_Success", "RT_sec_ERQ", "RT_sec_DERS", "RT_sec_IUS"))
      }
    }
  }

  if (all(names(df) != "ERQ_Supp")){
    if (any(names(df) == "Income")) {
      if (all(df$Choice == "Neither")){
        df <- subset(df,
                     select=c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                              "IntBefore", "IntAfter", "Failures",
                              "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                              "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                              "RT_sec_Choice", "RT_sec_IntBefore",
                              "RT_sec_IntAfter"))
      }
      if (any(df$Choice != "Neither")){
        df <- subset(df,
                     select=c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                              "IntBefore", "IntAfter", "IntReduce", "Effort", "Success", "Failures",
                              "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                              "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                              "RT_sec_Choice", "RT_sec_IntBefore",
                              "RT_sec_IntAfter", "RT_sec_IntReduce", "RT_sec_Effort",
                              "RT_sec_Success"))
      }
    }
    
    if (all(names(df) != "Income")) {
      if (all(df$Choice == "Neither")){
        df <- subset(df,
                     select = c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                                "IntBefore", "IntAfter", "Failures",
                                "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                                "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                                "RT_sec_Choice", "RT_sec_IntBefore",
                                "RT_sec_IntAfter"))
      }
      if (any(df$Choice != "Neither")){
        df <- subset(df,
                     select = c("PID", "Date", "Start_Time", "End_Time", "Condition", "Trial", "Stimulus", "Choice",
                                "IntBefore", "IntAfter", "IntReduce", "Effort", "Success", "Failures",
                                "ScreenWidth", "ScreenHeight", "WebAudio", "Browser", "Browser_Version", "MobileUsed",
                                "OS", "FullScreenUsed", "VSync_Rate_Avg", "VSync_Rate_SD",
                                "RT_sec_Choice", "RT_sec_IntBefore",
                                "RT_sec_IntAfter", "RT_sec_IntReduce", "RT_sec_Effort",
                                "RT_sec_Success"))
      }
    }
  }
  
  
  
  # ----- Output -----
  return(df)
  
}
```

The `here()` function should ideally Tidentify our upper-level project directory. So, `WorkDir` below should be a filepath that looks something like `C:/Users/.../Documents/GitHub/fright_night_study/", or where ever you store these files. Then we'll have additional variables store filepaths within that directory for where we're reading the data from and where we're sending data to. 

```{r Setting Working Directories}
  # Identifying our main directory
  WorkDir <- here::here()

  # Identifying specific directories to read and write from
  Import <- paste0(WorkDir, "/Data/Study_03/Source_hidden/")
  Export <- paste0(WorkDir, "/Data/Study_03/Raw/")
```

# ----- LOADING IN DATA -----

We're starting off my saving all file names above 20000 bytes (which is the rough cutoff for having completed enough of the study to be valid) to an array ...
```{r Specifying Data Source}
files <- list.files(Import,
                    full.names = T) %>%
         .[file.size(.) > 20000]
```

...and now we'll load all of that data into a singular dataframe using our custom data cleaner function.  
```{r Loading Data, warning = F}
## Iterating Through Each File in the Source}
for (FILE in 1:length(files)){
  
  ## If this is the first file we're reading ...
  if (FILE == 1){
    
    ## ... Define it as df
    df <- pavlovia_cleaner(files[FILE])
    
  }
  
  ## If this is a later file we're reading ...
  if (FILE > 1){
    
    ## ... Process it ...
    df_ <- pavlovia_cleaner(files[FILE])
    
    ## ... and then append it to df. 
    df <- bind_rows(df,
                    df_)
  }
  
  ## If this is the last iteration ...
  if (FILE == length(files)){
    
    ## Clean Our Space
    rm(pavlovia_cleaner, FILE, files, df_)
  }
}
```

# ----- TIME -----

I'm starting off by calculating how long each participant took to complete their session
```{r Assessing Time}
# Creating an Empty Column For Time
df$Time_Taken <- NA

# Iterating through each row and calculating time taken
for (ROW in 1:nrow(df)){
  
  # If Time in ROW is NA, skip
  if (!is.na(df$Start_Time[ROW])){
    
    # Convert time to a difftime object
    df$Time_Taken[ROW] <- strptime(df$End_Time[ROW], format = "%H:%M:%S") - strptime(df$Start_Time[ROW], format = "%H:%M:%S") %>%
                          as.numeric(units = "secs")
    
    # If the value is negative (indicating that their participation took place across days (i.e., midnight))
    if (df$Time_Taken[ROW] < 0 & !is.na(df$Time_Taken[ROW])){
      
      # Add the number of seconds in a day to get the true time it took. 
      df$Time_Taken[ROW] <- df$Time_Taken[ROW] + 86400
    }
  }
}

```

# ----- FILTERING DATA -----

Now we're filtering out non-completers, folks familiar with videos, and folks who did not complete the attention check correctly.
```{r Filtering Data}
## If people failed the attention check, get rid of them
df <- df[df$Attention_Check == 4,]

## If people are familiar with the stimuli, get rid of that stimulus
for (PID in unique(df$PID)){
  if (any(!is.na(df$Familiar_specific[df$PID == PID]))){
    array <- df$Familiar_specific[df$PID == PID & !is.na(df$PID)][1] %>%
             strsplit(" ") %>%
             as.data.frame() %>%
             .[,1]
    for (VID in 1:length(array)){
      df <- df[-which(df$PID == PID & !is.na(df$PID) & df$Stimulus == array[VID]),] 
    }
  }
}

## Drop rows with only NAs
df <- df[rowSums(is.na(df)) != ncol(df), ]
```

# ----- REPLACING PID -----

So that we can share this data publicly, I'll now replace each unique PID with another PID
```{r replacing PIDs}
for (PID in unique(df$PID)){
  df$PID[df$PID == PID & !is.na(df$PID)] <- 
    sprintf(fmt = "%03d", which(unique(df$PID) == PID)) %>%
                           paste0("sub-", .)
}
```

```{r Replacing the one subject missing a PID manually}
df$PID[is.na(df$PID)] <- "sub-243"
```

```{r Writing File}
write.csv(df, paste0(Export, "df.csv"))
```
